partial: An R Package for Creating Partial Dependence Plots

### 2016-08-08 manuscript/greenwell.tex
minor edits

The \CRANpkg{plotmo} package \citep{plotmo-pkg} has come a long way in this regard. According to the author, \pkg{plotmo} constructs "a poor man's partial dependence plot." In particular, it plots a model's response when varying one or two predictors while holding the other predictors constant (continuous features are fixed at their median value, while factors are held at their first level). These plots allow for up to two variables at a time and are less accurate than PDPs, but are faster to construct! For additive models (i.e., no interactions), these plots are identical in shape to partial dependence plots.

>>>>

The \CRANpkg{plotmo} package \citep{plotmo-pkg} is one alternative to \pkg{partial}. According to the author, \pkg{plotmo} constructs "a poor man's partial dependence plot." In particular, it plots a model's response when varying one or two predictors while holding the other predictors in the model constant (continuous features are fixed at their median value, while factors are held at their first level). These plots allow for up to two variables at a time and are less accurate than PDPs, but are faster to construct. For additive models (i.e., no interactions), these plots are identical in shape to partial dependence plots.
